Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-24 doc/bcspaper/article.tex
Added subfig caption=false to bring down to 6 pages
Fixed percentages in table 1

\usepackage{wrapfig}
\usepackage{subfig}

@@

\subfloat{
\includegraphics[width=0.45\textwidth]{figures/review_corescs.png}
}
\subfloat{
\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
}
\caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}

@@

\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}

\begin{tabular}{p{2.4cm}p{1.5cm}p{1.5cm}p{1.5cm}}
\hline\noalign{\smallskip}
Classes & Recall & Precision & F-measure  \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Case Study      &   24.3\verb|%|    &    24.5\verb|%|     &   24.4\verb|%| \\
Correspondence  &   {\bf  54.5\verb|%|}    &    {\bf 50.5\verb|%|}    &    {\bf 52.4\verb|%|} \\ 
Essay           &   45.0\verb|%|     &   46.2\verb|%|    &    45.6\verb|%| \\
Opinion         &   24.7\verb|%|    &    23.5\verb|%|  &      24.1\verb|%| \\   
Perspective     &   25.5\verb|%|  &      30.4\verb|%|  &       27.7\verb|%| \\
Research        &   {\bf 70.0\verb|%|}    &    {\bf 61.9\verb|%|}    &    {\bf 65.7\verb|%|} \\
Review          &  {\bf 63.1\verb|%|}     &   {\bf 62.5\verb|%|}     &   {\bf 62.8\verb|%|} \\
Viewpoint       &     14.9\verb|%|     &   15.7\verb|%|  &      15.3\verb|%| \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}

>>>>

\usepackage{wrapfig}
\usepackage[caption=false]{subfig}

@@

\subfloat{
\includegraphics[width=0.45\textwidth]{figures/review_corescs.png}
}
\subfloat{
\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
}
\caption{The CoreSC content of a review paper (left) and a research paper (right) randomly selected from the corpus}

@@

\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment. Top paper types in bold.}

\begin{tabular}{p{2.4cm}p{2.0cm}p{2.0cm}p{2.5cm}}
\hline\noalign{\smallskip}
Classes & Recall(\verb|%|) & Precision(\verb|%|)& F-measure(\verb|%|) \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Case Study      &   24.3    &    24.5     &   24.4 \\
Correspondence  &   {\bf  54.5}    &    {\bf 50.5}    &    {\bf 52.4} \\ 
Essay           &   45.0     &   46.2    &    45.6 \\
Opinion         &   24.7    &    23.5  &      24.1 \\   
Perspective     &   25.5  &      30.4  &       27.7 \\
Research        &   {\bf 70.0}    &    {\bf 61.9}    &    {\bf 65.7} \\
Review          &  {\bf 63.1}     &   {\bf 62.5}     &   {\bf 62.8} \\
Viewpoint       &     14.9     &   15.7  &      15.3 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
